Deployable Probabilistic Programming

### 2019-04-17 paper/paper.tex
in progress, broken

\section{Related Work}
Probabilistic programming languages \cite{GS15}, \cite{MPY+18},
\cite{Stan17}, \cite{GGS19}.

>>>>

\section{Related Work}

Our work is related to three interconnected areas of research:
\begin{enumerate}
	\item Design and implementation of probabilistic programming
		languages. 
	\item Integration and interoperability between probabilistic
		programming models and the surrounding software
		systems.
	\item Differentiable programming for machine learning.
\end{enumerate}

Probabilistic programming is traditionally associated with
design and implemenetation of probabilistic programming
languages. An apparent justification for a new programming
language is that a probabilistic program has a different
semantics~\cite{GHNR14} than a `regular' program of similar
structure. Goodman and Stuhlm\"uller~\cite{GS15} offer a
systematic approach to design and implementation of
probabilistic programming languages based on extension of the
syntax of a (subset of) regular programming language and
transformational compilation to continuation-passing form. Van
de Meent et al~\cite{MPY+18} give a comprehensive overview of
available choices of design and implementation of first-order
and higher-order probabilistic programming languages.
Stan~\cite{Stan17} is built around an imperative probabilistic
programming language with program structure tuned for most
efficient execution of inference on the model.
SlicStan~\cite{GGS19} is built on top of Stan as a
source-to-source compiler, providing the model developer with
a more intuitive language while retaining performance benefits
of Stan.
